%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Technical Lead} % Job title
{Hashgreen Inc.} % Organization
{Taipei, Taiwan} % Location
{Sep. 2021 - Nov. 2024} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Led a 5-member team implementing agile and DevOps practices from scratch, using JIRA for task tracking, GitHub Actions for CI/CD, and Docker for containerization, improving workflow efficiency by 20\%.}
    \item {Developed and deployed a decentralized exchange (DEX) and SwapDeFi solution using Chia blockchain. Created backend services with Golang, gRPC for service communication, Gin as web framework, and utilized AWS EKS for Kubernetes deployment, enhancing service stability and scalability.}
    \item {Designed Blockchain Explorer and Node as a Service using microservices architecture, employing Docker, Helm, and Kafka for real-time data streaming and container orchestration. This setup enabled users to query blockchain data and receive real-time transaction updates efficiently, significantly enhancing system transparency and data accessibility.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Site Reliability Engineer} % Job title
{Newtype Games Limited} % Organization
{Taipei, Taiwan} % Location
{Jun. 2020 - Feb. 2021} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Implemented a monitoring and log system using ELK Stack (Elasticsearch, Logstash, Kibana), integrated with Grafana and Prometheus, enabling engineers to analyze logs directly in Kibana, reducing reliance on server access and improving diagnostic efficiency.}
    \item {Developed a configuration management prototype similar to HashiCorp Vault, focused on secure application configuration and encryption. This prototype enhanced configuration security management before a company-wide layoff halted further development.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Software Engineer in Product Licensing Service (Contractor)} % Job title
{TrendMicro Inc.} % Organization
{Taipei, Taiwan} % Location
{Oct. 2019 - Mar. 2020} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Created a self-service website with RBAC for user permissions and activity tracking using React for frontend and .NET Core for backend, deployed on AWS EKS, utilizing Helm for Kubernetes orchestration, which improved system responsiveness and security.}
    \item {Built an SSO security enhancement service using Kafka for publish-subscribe decoupling, integrated with device detection and alerts, which significantly strengthened authentication security.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{System Engineer} % Job title
{President Futures Co. Ltd} % Organization
{Taipei, Taiwan} % Location
{Sep. 2016 - Apr. 2019} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Developed a bulletin system using .NET Core RESTful API and Angular 2 for the management interface, integrated with RabbitMQ for real-time messaging, improving user engagement by 30\%.}
    \item {Implemented a GitLab-based CI pipeline with Docker for containerization, automating build, test, and deployment processes, which reduced development cycle time by 20\% and improved version control efficiency.}
  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
