%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Technical Lead} % Job title
{Hashgreen Inc.} % Organization
{Taipei, Taiwan} % Location
{Sep. 2021 - Present} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {At Hashgreen Inc., I led a team of five engineers, focusing on optimizing our software engineering workflows and fostering an Agile and DevOps culture. My role involved conducting technical sharing sessions and authoring blog posts to promote knowledge sharing and continuous learning within the team. This approach not only improved our operational efficiency but also enhanced team collaboration and innovation.}
    \item {I initially engaged in a pioneering project involving a decentralized exchange (DEX) based on the Chia blockchain. After operating the DEX for about three months, the project was discontinued due to a strategic pivot. We then shifted our focus to developing a Swap DeFi solution utilizing the same technology stack. Throughout this transition, my role involved splitting our efforts into two main segments: Infrastructure (Infra) and Applications (Application), with my primary responsibility being the development and maintenance of the infrastructure.}
    \item {The infrastructure component encompassed two core services: Blockchain Explorer and Node as a Service. Blockchain Explorer served as a tool enabling users to query blockchain data effectively, enhancing transparency and accessibility. Meanwhile, Node as a Service provided real-time block and transaction information, operating similarly to services like Infura or QuickNode. Throughout the development of these services, we adopted a microservices architecture, significantly enhancing the system's scalability and maintainability while ensuring high availability and security.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Site Reliability Engineer} % Job title
{Newtype Games Limited} % Organization
{Taipei, Taiwan} % Location
{Jun. 2020 - Feb. 2021} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {At Newtype Games, I spearheaded the design and deployment of a sophisticated monitoring and log collection system comprising the ELK Stack (Elasticsearch, Logstash, Kibana), Grafana, and Prometheus. This initiative was aimed at enhancing application performance monitoring and health assessment, crucial for maintaining system stability and reliability. The deployment of the ELK Stack allowed for centralized collection and analysis of application logs, playing a key role in swiftly diagnosing and resolving potential application issues. Additionally, the integration of Prometheus facilitated the collection of various performance metrics, which were instrumental in monitoring real-time system performance and implementing necessary optimizations.}
    \item {In another significant project, I developed a universal service entry point using Go, which significantly enhanced the security and accessibility of application configurations. This development centralized the management of application settings, boosting the security and simplification of configuration management, while also ensuring secure access to sensitive information.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Software Engineer in Product Licensing Service (Contractor)} % Job title
{TrendMicro Inc.} % Organization
{Taipei, Taiwan} % Location
{Oct. 2019 - Mar. 2020} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {I designed and developed a self-service website that incorporates rights management through Role-Based Access Control (RBAC) and tracks user activity history. The project utilized React for the frontend and .NET Core for backend services, with deployment on AWS EKS facilitated by Helm. This implementation enhanced user interface responsiveness and security while ensuring scalable cloud deployment.}
    \item {I spearheaded the design of a service to bolster single sign-on (SSO) security by integrating device detection and alert capabilities. This service was built as a .NET Core console application and leveraged Kafka’s publish/subscribe mechanisms for effective system decoupling, enhancing system security and reliability.}
    \item {I developed a system focused on recording and querying user authentication logs. The system was architected using RESTful API services built with .NET Core, employing a combination of Graylog, Elasticsearch, and Fluentd to store and analyze audit logs. This setup facilitated robust data integrity and insightful audit trail analysis.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{System Engineer} % Job title
{President Futures Co. Ltd} % Organization
{Taipei, Taiwan} % Location
{Sep. 2016 - Apr. 2019} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {I designed and implemented a bulletin system, utilizing .NET Core for developing a RESTful API and Angular 2 for creating the management interface. The system integrates client messaging functionality using RabbitMQ, enhancing communication efficiency and user engagement.}
    \item {I developed a modular futures trading platform using WPF and Prism, which was tailored to meet specific operational requirements. This custom solution provided a robust and flexible trading environment, significantly enhancing trading efficiency and user experience.}
    \item {I conducted extensive research and implemented a version control system (VCS) and continuous integration (CI) practices, utilizing Docker to deploy GitLab. My efforts led to the successful onboarding and training of the development team, markedly improving overall development processes and efficiency.}
  \end{cvitems}
}

%---------------------------------------------------------
\end{cventries}
